Rodent trapping studies to understand the prevalence of zoonotic disease in West Africa: A scoping review.

### 2021-08-31 reports/manuscript_v2.Rmd
updating report

## Rodent presence, absence, abundance
  * 73,164 small mammals were trapped (592 were trapped outside of West African countries), 2,830 (4%) trapped individuals were identified to order level (Rodentia), 7,760 (11%) were identified to genus level, the remaining 62,574 (85%) were identified to species level. 
  * In studies reporting the number of trap nights the median trap success rate of traps placed in or around buildings was 13% (IQR 6-24%), this compares to a median trap success rate of 3% (IQR 1-9%) in other habitats.
  * Of the 147 distinct identified species trapped (see Supplementary Material 3) the majority were from the order Rodentia (112). Muridae (82) represented the largest family of rodents, followed by, Sciuridae (10), Gliridae and Nesomyidae (both 6), Ctenodactylidae and Anomaluridae (2) and Dipodidae, Hystricidae and Thryonomidae (all 1). The remaining 34 species came from the orders of the Soricomorpha (30), Erinaceomorpha (2) and Afrosoricida (1).
  * The most commonly trapped genera of rodents were Mastomys sp. (27,072, 38.5%), Rattus sp. (10,191, 14.5%), Mus sp. (8,624, 12.3%), Arvicanthis sp. (5,821, 8.3%) and Praomys sp. (5,409, 7.7%). At species level Mastomys natalensis (11,221, 17.9%), Rattus rattus (8,578, 13.7%), Mastomys erythroleucus (7,379, 11.8%), Mus musculus (6,245, 10%), Arvicanthis niloticus (5,497, 8.8%) and Mastomys huberti (4,699, 7.5%) were the most commonly trapped. 
  * Presence and absence maps for the six most commonly trapped species are compared to GBIF and IUCN data. (Need to do this)
  * The number of individuals trapped provides a measure of abundance, the interpretation of this is limited by incomplete reporting on the trapping effort (i.e. number of trap nights) within a study. The most abundant species at presence locations were … (Need to do this. I will explore the number of individuals trapped by species, I imagine it will show that if a species is detected at a site the most abundant ones will be the synanthropic species such as mus, rattus etc. while the more specialised species will be less abundant in areas where they are detected)

Figure 3 - Three plots side by side with 6 rows, one each for the most commonly trapped species Panel A - presence/absence from this review, Panel B - presence/absence from GBIF, Panel C - Species range from IUCN

Figure 3 - **Panel A** shows the presence and absence of the 6 most commonly trapped rodent species from the current study. The perimeter polygon (blue) is the convex hull of the observation points produced from presence only data. **Panel B**

>>>>

## Rodent presence, absence, abundance
  * 73,164 small mammals were trapped (592 were trapped outside of West African countries), 2,830 (4%) trapped individuals were identified to order level (Rodentia), 7,760 (11%) were identified to genus level, the remaining 62,574 (85%) were identified to species level. 
  * In studies reporting the number of trap nights the median trap success rate of traps placed in or around buildings was 13% (IQR 6-24%), this compares to a median trap success rate of 3% (IQR 1-9%) in other habitats.
  * Of the 147 distinct identified species trapped (see Supplementary Material 3) the majority were from the order Rodentia (112). Muridae (82) represented the largest family of rodents, followed by, Sciuridae (10), Gliridae and Nesomyidae (both 6), Ctenodactylidae and Anomaluridae (2) and Dipodidae, Hystricidae and Thryonomidae (all 1). The remaining 34 species came from the orders of the Soricomorpha (30), Erinaceomorpha (2) and Afrosoricida (1).
  * The most commonly trapped genera of rodents were Mastomys sp. (27,079, 37.7%), Rattus sp. (11,472, 16.1%), Mus sp. (8,624, 12.0%), Arvicanthis sp. (5,821, 8.1%) and Praomys sp. (5,409, 7.5%). At species level Mastomys natalensis (11,116, 17.4%), Rattus rattus (9,959, 15.6%), Mastomys erythroleucus (7,386, 11.6%), Mus musculus (6,245, 9.8%), Arvicanthis niloticus (5,497, 8.6%), Mastomys huberti (4,699, 7.4%) and Praomys daltoni (1,854, 2.9%) were the most commonly trapped. 
  * Presence and absence maps for the seven most commonly trapped species are compared to GBIF and IUCN data in Figure 3 Panel A-G. 
  * The number of individuals trapped provides a measure of abundance, the interpretation of this is limited by incomplete reporting on the trapping effort (i.e. number of trap nights) within a study. The most abundant species at presence locations were … (Need to do this. I will explore the number of individuals trapped by species, I imagine it will show that if a species is detected at a site the most abundant ones will be the synanthropic species such as mus, rattus etc. while the more specialised species will be less abundant in areas where they are detected)

```{r, figure_3, layout = "l_page", echo=FALSE}
knitr::include_graphics(here("figures", "Figure_3.png"))
```

Figure 3 - Three plots side by side with 7 rows, one each for the most commonly trapped species Panel A - presence/absence from this review, Panel B - presence/absence from GBIF, Panel C - Species range from IUCN

Figure 3 - **Panel A-G** shows the presence and absence of the 7 most commonly trapped rodent species from the current study.
